En garde! Unguarded iteration for reversible computation in the Delay monad\thanks{Supported by organization x.}

### 2019-04-29 mpc19/paper.tex
interpretation of terms

\usepackage{proof}
\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{fancyvrb}

@@

@@

\section{TODO} % (fold)
\label{sec:todo}
Robin:
\begin{itemize}
  \item Make pictures! 
  \begin{itemize}
    \item Hasegawa trace from iterator.
  \end{itemize}
  \item Conclusion
  \begin{itemize}
    \item Related work: Kleisli category of the Delay monad is a join
    restriction category, inverse category of a join restriction category is a
    join inverse category; already known to be dagger-traced under certain
    conditions.
    \item Future work: Semantics of time invertible programming. Extension of
    the work on the Kleisli category of the Delay monad beyond $\Set$ to other
    (more general) categories, e.g. topoi.
  \end{itemize}
\end{itemize}
Niccolò: 
\begin{itemize}
  \item Fix the syntax to be closer to ordinary presentations (but do describe 
  how it is realized in Agda).
  \item Finish the section about trace and iteration.
  \item Remind the reader about double lines of coinductive definitions.
  \item Swap types in Elgot iterator.
\end{itemize}
Both:
\begin{itemize}
  \item \textbf{Important:} Come up with a punnier title! (Something about 
  delays and daggers).
\end{itemize}
% section todo (end)

@@

>>>>

\usepackage{proof}
\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{fancyvrb}
\usepackage{stmaryrd}

@@

% Semantics
\newcommand{\semTy}[1]{{\llbracket #1 \rrbracket}_\mathsf{Ty}}
\newcommand{\semMu}[1]{{\llbracket #1 \rrbracket}_\mu}
\newcommand{\semTm}[1]{{\llbracket #1 \rrbracket}_\lr}

@@

\section{TODO} % (fold)
\label{sec:todo}
Robin:
\begin{itemize}
  \item Make pictures! 
  \begin{itemize}
    \item Hasegawa trace from iterator.
  \end{itemize}
  \item Conclusion
  \begin{itemize}
    \item Related work: Kleisli category of the Delay monad is a join
    restriction category, inverse category of a join restriction category is a
    join inverse category; already known to be dagger-traced under certain
    conditions.
    \item Future work: Semantics of time invertible programming. Extension of
    the work on the Kleisli category of the Delay monad beyond $\Set$ to other
    (more general) categories, e.g. topoi.
  \end{itemize}
\end{itemize}

% section todo (end)

@@

In this section, we provide some details on the interpretation of the
syntax of \Pio, presented in Section \ref{sec:syntax}, into the
category $\Inv\Dapprox$. Types of \Pio\ are modelled as objects of
$\Inv\Dapprox$, which are types of the metatheory. In Agda, the
interpretation of types $\semTy -$ takes in input a \Pio\ type
$A : \Ty\,n$ and an environment $\rho : \mathsf{Fin}\,n \to \Set$
giving semantics to each variable in context. The interpretation is
mutually inductively defined together with the operation $\semMu -$
giving semantics to the $\mu$ type former.
\[
\begin{array}{lll}
\semTy \Z & \rho & = 0 \\
\semTy {A \oplus B} & \rho & = \semTy A \,\rho+ \semTy B  \, \rho\\
\semTy \I & \rho & = 1 \\
\semTy {A \otimes B} & \rho & = \semTy A \,\rho \times \semTy B \,\rho\\
\semTy {\Var\,i} & \rho & = \rho\, i \\
\semTy {\mu A} & \rho & = \semMu A \,\rho
\end{array}
\qquad \qquad
\infer{\mathsf{semFold} \,x : \semMu A\,\rho}{x : \semTy A \, \rho}
\]

Terms of \Pio\ are modelled as morphism of $\Inv\Dapprox$,
i.e. partial isomorphisms. Formally, we define an operation:
\[
\semTm - : (A \lr B) \to 
\]
